Evaluation of performances

### 2021-11-14 analysis/eval-performance.Rmd

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  # replace iter IDs by individual fold names
  dplyr::mutate(iter = as.character(iter)) %>%
  dplyr::mutate(iter = case_when(
    learner.id == "XGBOOST MBO CMIM" & iter == 1 ~ "Luiando",
    learner.id == "XGBOOST MBO CMIM" & iter == 2 ~ "Laukiz1",
    learner.id == "XGBOOST MBO CMIM" & iter == 3 ~ "Oiartzun",
    learner.id == "XGBOOST MBO CMIM" & iter == 4 ~ "Laukiz2",

    learner.id == "SVM MBO Relief" & iter == 1 ~ "Laukiz1",
    learner.id == "SVM MBO Relief" & iter == 2 ~ "Oiartzun",
    learner.id == "SVM MBO Relief" & iter == 3 ~ "Luiando",
    learner.id == "SVM MBO Relief" & iter == 4 ~ "Laukiz2",

    learner.id == "RF MBO Relief" & iter == 1 ~ "Luiando",
    learner.id == "RF MBO Relief" & iter == 2 ~ "Laukiz2",
    learner.id == "RF MBO Relief" & iter == 3 ~ "Laukiz1",
    learner.id == "RF MBO Relief" & iter == 4 ~ "Oiartzun",

    TRUE ~ as.character(iter)
  )) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::mutate(fw.perc = fw.perc * 100) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(`Test Plot` = as.character(Plot)) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF \\\\ Relief" = "RF MBO Relief", "XGB \\\\ CMIM" = "XGBOOST MBO CMIM",
    "SVM \\\\ Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(`Test Plot` = as.character(`Test Plot`)) %>%
  dplyr::mutate("Features (\\#)" = case_when(
    # numbers here are the respective sums of the training sets (without the mentioned plot acting as the test set)
    `Test Plot` == "Laukiz1" ~ paste0(as.character(ceiling((`Features (\\%)` * 1249) / 100)), "/1249"),
    `Test Plot` == "Laukiz2" ~ paste0(as.character(ceiling((`Features (\\%)` * 1357) / 100)), "/1357"),
    `Test Plot` == "Luiando" ~ paste0(as.character(ceiling((`Features (\\%)` * 1507) / 100)), "/1507"),
    `Test Plot` == "Oiartzun" ~ paste0(as.character(ceiling((`Features (\\%)` * 1311) / 100)), "/1311"),
  )) %>%
  dplyr::group_by(Learner) %>%
  dplyr::arrange(Learner, `Test Plot`) %>%
  dplyr::select(Learner, `Test Plot`, "Features (\\%)", "Features (\\#)")

>>>>

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  # replace iter IDs by individual fold names
  dplyr::mutate(iter = as.character(iter)) %>%
  dplyr::mutate(iter = case_when(
    learner.id == "XGBOOST MBO Borda" & iter == 1 ~ "Luiando",
    learner.id == "XGBOOST MBO Borda" & iter == 2 ~ "Laukiz1",
    learner.id == "XGBOOST MBO Borda" & iter == 3 ~ "Oiartzun",
    learner.id == "XGBOOST MBO Borda" & iter == 4 ~ "Laukiz2",

    learner.id == "SVM MBO Car" & iter == 1 ~ "Laukiz1",
    learner.id == "SVM MBO Car" & iter == 2 ~ "Oiartzun",
    learner.id == "SVM MBO Car" & iter == 3 ~ "Luiando",
    learner.id == "SVM MBO Car" & iter == 4 ~ "Laukiz2",

    learner.id == "RF MBO Car" & iter == 1 ~ "Luiando",
    learner.id == "RF MBO Car" & iter == 2 ~ "Laukiz2",
    learner.id == "RF MBO Car" & iter == 3 ~ "Laukiz1",
    learner.id == "RF MBO Car" & iter == 4 ~ "Oiartzun",

    TRUE ~ as.character(iter)
  )) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::mutate(fw.perc = fw.perc * 100) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(`Test Plot` = as.character(Plot)) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF \\\\ Car" = "RF MBO Car", "XGB \\\\ Borda" = "XGBOOST MBO Borda",
    "SVM \\\\ Car" = "SVM MBO Car"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(`Test Plot` = as.character(`Test Plot`)) %>%
  dplyr::mutate("Features (\\#)" = case_when(
    # numbers here are the respective sums of the training sets (without the mentioned plot acting as the test set)
    `Test Plot` == "Laukiz1" ~ paste0(as.character(ceiling((`Features (\\%)` * 1249) / 100)), "/1249"),
    `Test Plot` == "Laukiz2" ~ paste0(as.character(ceiling((`Features (\\%)` * 1357) / 100)), "/1357"),
    `Test Plot` == "Luiando" ~ paste0(as.character(ceiling((`Features (\\%)` * 1507) / 100)), "/1507"),
    `Test Plot` == "Oiartzun" ~ paste0(as.character(ceiling((`Features (\\%)` * 1311) / 100)), "/1311"),
  )) %>%
  dplyr::group_by(Learner) %>%
  dplyr::arrange(Learner, `Test Plot`) %>%
  dplyr::select(Learner, `Test Plot`, "Features (\\%)", "Features (\\#)")
